On multilevel constraint decomposition methods \\ for nonlinear and nonlocal variational inequalities

### 2021-07-01 paper/mcd2.tex
Make a bit more progress.

\section{$p$-coercive variational inequalities} \label{sec:vi}

@@

However, not all VIs correspond to optimization problems.  For example, consider the following problem of porous-medium type.

\begin{example}  Suppose $\Omega \subset \RR^d$ is bounded and open with polygonal boundary.  Let $\cV = H_0^1(\Omega)$ and consider $\cK = \{v\ge 0\} \subset \cV$.  For $g\in \cV'$ and $u$ in $\cK$ let
\begin{equation}
\ip{f(u)}{v} = \int_\Omega (1+e^{-u}) \grad u \cdot \grad v\,dx - \ip{g}{v}. \label{eq:nongradientexample}
\end{equation}
It is easy to see that $|\ip{f(u)}{v}| \le (c \|u\|_{\cV} + \|g\|_{\cV'}) \|v\|_{\cV}$, thus that $f:\cK \to \cV'$ is continuous.  FIXME IS IT $2$-coercive?  FIXME $f\ne F'$
\end{example}

@@

\section{Multilevel constraint decomposition algorithms} \label{sec:algorithms}

FIXME state the decomposition, the basis algorithm, the FAS version which has $O(m)$ residual evaluation complexity on each level

>>>>

\section{Coercive variational inequalities and constraint decomposition} \label{sec:vi}

@@

However, not all VIs correspond to optimization problems.  For example, consider the following steady advection-diffusion problem.

\begin{example}  Suppose $\Omega \subset \RR^d$ is bounded and open with polygonal boundary.  Let $\cV = H_0^1(\Omega)$ and consider $\cK = \{v\ge 0\} \subset \cV$.  For $g\in \cV'$, $\bX \in L^\infty(\Omega)^d$, and $u$ in $\cK$ let
\begin{equation}
\ip{f(u)}{v} = \int_\Omega \grad u \cdot \grad v\,dx - (\bX \cdot \grad u) v - \ip{g}{v}. \label{eq:nongradientexample}
\end{equation}
FIXME POINT OUT THAT IS STEADY ADVECTION-DIFFUSION VI; IF $\bX=0$ THEN IT IS OPTIMIZATION BUT OTHERWISE NOT; ALWAYS CONTINUOUS; IF $\bX$ IS SMALL THEN $2$-coercive; It is easy to see that $|\ip{f(u)}{v}| \le (c \|u\|_{\cV} + \|g\|_{\cV'}) \|v\|_{\cV}$, thus that $f:\cK \to \cV'$ is continuous.
\end{example}

Other examples of VI problems which are not of optimization type are found in ice sheet applications \cite{Calvoetal2002,JouvetBueler2012} and other geophysical fluids problems \cite{Bueler2021conservation}.

@@

The multilevel algorithms we consider later are based on both subspace \cite{Xu1992} and constraint \cite{Tai2003} decompositions, as follows.  Suppose $\cV_i \subset \cV$ are $m<\infty$ subspaces so that
\begin{equation}
\cV = \sum_{i=1}^m \cV_i \label{eq:subspacedecomp}
\end{equation}
in the sense that if $w \in \cV$ then there exist $w_i \in \cV_i$ so that $w = \sum_i w_i$.  Suppose further that $\cK_i \subset \cV$ are nonempty, closed, and convex subsets such that
\begin{equation}
\cK_i \subset \cV_i \qquad \text{and} \qquad \cK = \sum_{i=1}^m \cK_i. \label{eq:constraintdecomp}
\end{equation}
The sum in \eqref{eq:constraintdecomp} is required to hold in two senses: \emph{(i)}~if $w \in \cK$ then there exist $w_i \in \cK_i$ so that $w = \sum_i w_i$, and \emph{(ii)}~if $z_i \in \cK_i$ for each $i$ then $\sum_i z_i \in \cK$.  (The latter sense is automatic in \eqref{eq:subspacedecomp} because $\cV_i$ are subspaces.)  Neither decomposition is unique in general.  Note that $\cK_i \not\subset \cK$ in most applications.

In practice the space $\cV$ will be a finite-dimensional finite element (FE) space because we will solve VI \eqref{eq:vi} over a mesh.  We FIXME triangulation etc. Though our

\begin{example}  FIXME $\cV_i$ are 1d spaces on a single level; $\psi,\cK,\cK_i$ for obstacle problem; note $\cK_i \not\subset \cK$ when $\psi>0$
\end{example}

FIXME state the basic algorithm

\section{Multilevel constraint decomposition algorithms} \label{sec:multilevel}

FIXME state essentially Algorithm 4.7 \cite{GraeserKornhuber2009} but with $\text{V}(\nu_1,\nu_2)$ cycles which works for linear; observe that up-smoothing is more efficient; state the FAS version which has $O(m)$ residual evaluation complexity on each level
